Lapse & Vision Loss PS Analysis

### 2025-06-23 analysis.Rmd
update analysis

library(cobalt)
library(dplyr)
library(gee)
library(ggplot2)
library(kableExtra)
library(margins)
library(MatchIt)
library(purrr)
library(readr)
library(survey)
library(twang)
library(WeightIt)

@@

  } else if (method_name == "subclass_glm") {
    matched_data <- MatchIt::match_data(method_result$result, subclass = "subclass")
    design <- svydesign(ids = ~e_mrn_deidentified, data = matched_data, weights = ~weights)
    design <- postStratify(design, ~subclass, xtabs(~subclass, data = matched_data))

  } else {
    matched_data <- MatchIt::get_matches(method_result$result)
    design <- svydesign(ids = ~e_mrn_deidentified, data = matched_data, weights = ~1)
  }

@@

saveRDS(final_models, file.path(ps_dir, paste0("ps_analysis_models.rds")))
saveRDS(final_results, file.path(ps_dir, paste0("ps_results_summary.rds")))
```

@@

```{r paper_table}

output_model <- all_results$twang_gbm

>>>>

library(broom)
library(cobalt)
library(dplyr)
library(flextable)
library(gee)
library(ggplot2)
library(gt)
library(gtsummary)
library(kableExtra)
library(jtools)
library(margins)
library(MatchIt)
library(purrr)
library(readr)
library(survey)
library(twang)
library(WeightIt)

@@

  } else if (method_name == "subclass_glm") {
    matched_data <- MatchIt::match_data(method_result$result, subclass = "subclass")
    design <- svydesign(ids = ~e_mrn_deidentified, data = matched_data, weights = ~weights)
    design <- postStratify(design, ~subclass, xtabs(~subclass, data = matched_data))
  } else {
    matched_data <- MatchIt::get_matches(method_result$result)
    design <- svydesign(ids = ~e_mrn_deidentified, data = matched_data, weights = ~1)
  }

@@

saveRDS(model_objects, file.path(ps_dir, paste0("ps_analysis_models.rds")))
saveRDS(final_results, file.path(ps_dir, paste0("ps_results_summary.rds")))
```

@@

```{r paper_table}
# model_objects <- readRDS(file.path(ps_dir, paste0("ps_analysis_models.rds")))

output_model <- model_objects$twang_gbm$full

tidy_output_model_formatted <- function(model, digits = 2) {
  tidy(model, exponentiate = TRUE, conf.int = TRUE) |>
    mutate(
      estimate = round(estimate, digits),
      std.error = round(std.error, digits),
      statistic = round(statistic, digits),
      conf.low = round(conf.low, digits),
      conf.high = round(conf.high, digits),
      p.value = round(p.value, digits + 1),
      # OR_CI = paste0(estimate, " (", conf.low, ", ", conf.high, ")"),
      p.value.sum = case_when(
        p.value < 0.001 ~ "<.001",
        TRUE ~ formatC(p.value, format="f", digits = 3)
      )
    )
}
tidy_output_model <- tidy_output_model_formatted(output_model)
tidy_output_model
flextable(tidy_output_model) |> save_as_docx(path = file.path(ps_dir, paste0("output_model_tidy_formatted.docx")))
